---
title: "Executive Summary"
format: html
editor: visual
---

<!--# Timestamp: leave this in to automatically track when a file is rendered -->

*Rendered at `r format(Sys.time(), '%I:%M %p, %b. %d, %Y')`*

<!--# Contact info: leave author/reporter/editor contact info here -->

*Ryan Thornburg ([ryan.thornburg\@unc.edu](mailto:ryan.thornburg@unc.edu){.email})*

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(here)
library(DT)
library(janitor)
library(plotly)

source(here("etl","load_data.R"))
```

## Which state and contests did we cover?

```{r}
#| message: false
#| code-fold: true
all_mentions %>% 
  group_by(state, contest) %>%
  summarize(mentions=n())  %>% 
  mutate(mentions = case_when(
    contest == "Butler" ~ 0,
    TRUE ~ as.numeric(mentions))
    ) %>%
  datatable(options = list(dom='t',
                         pageLength = 27),
            colnames = c('State', 'Contest', 'Mentions'),
          rownames = FALSE)
```

## How many articles did we code?

```{r}
#| code-fold: true
#| 
inc_unique_articles <- incumbents %>% 
  filter(duplicative_publication_of_previous_article == "0")

nrow(inc_unique_articles)
```

1,646 articles that mention incumbents that are coded as unique.

```{r}
#| code-fold: true

ninc_unique_articles <- non_incumbents %>% filter(duplicative_publication_of_previous_article == "0" & duplicative_of_incumbent_article == "0")

nrow(ninc_unique_articles)
```

328 articles that mention non-incumbents that are coded as unique.

We did not determine whether an article was unique across the whole data set. For example, if an article mentions two different challengers, it would appear in our data twice.

## What types of articles did we have?

1 = news story

2 = opinion or editorial

3 = letter to the editor

4 = advertisement/notification

99 = other

```{r}
#| code-fold: true

combined_unique_articles <- bind_rows(inc_unique_articles, ninc_unique_articles) 

combined_unique_articles %>%
    tabyl(type_of_article) %>%
  datatable(options = list(dom='t'),
            rownames = FALSE,
            colnames = c('Type', '# of articles', '% of articles')) %>%
  formatPercentage('percent', 2) %>%
  formatRound('n', digits = 0)
  

```

## How competitive was each contest we analyzed?

*Note: In Lake County, Oregon, there was no incumbent following the resignation of the previous district attorney in 2018. In other contests marked as "open," the incumbent did not run but did receive news coverage.*

```{r}
#| code-fold: true
#| message: false

competitiveness %>%
  select(state, contest, type, incumbents, non_incumbents) %>% 
  datatable(options = list(dom='t',
                         pageLength = 27),
            colnames = c('State', 'Contest', 'Competitiveness', 'Incumbents', 'Challengers'),
          rownames = FALSE) 

```

```{r}
#| code-fold: true
#| include: false

save.image(here("data","processed","index.RData"))

```
